Dirac neutrino mass generation from Majorana messenger

### 2019-08-06 draft.tex
lc

On the other hand, we assume that the heavy Majorana fermions are already in the diagonal basis defined as $
\begin{pmatrix}
  \psi_1 &
  \psi_2 &
  \psi_3
\end{pmatrix}^{\operatorname{T}}
$, with masses $M_{\psi_a}$ ($a=1,2,3$).
\section{Neutrinos}
\label{sec:Neutrinos}
%
\begin{figure}
\centering
\includegraphics[scale=0.75]{Neutrino_Loop.pdf}
\caption{One-loop generation of Dirac neutrino mass}
\label{fig:zee}
\end{figure}
%
 The Dirac neutrino mass matrix in this model is generated at one loop-level according to the diagram in  fig.~\ref{fig:zee}. The expression for $\mathcal{M}_{\nu}$ is given by~\cite{Reig:2018mdk}
%
\begin{align}
(\mathcal{M}_{\nu})_{ij} = \frac{\mu \upsilon_{H} \upsilon_{S}}{32 \pi^{2}} \sum_{a=1}^{3} \frac{h_{i a} M_{\psi_{a}}y^{\dagger}_{a j}} {m_{\chi_{R_2}}^{2}-m_{\chi_{R_1}}^{2}} \left[ F\left( \frac{m_{\chi_{R_2}}^{2}}{M_{\psi_{a}}} \right) - F\left( \frac{m_{\chi_{R_1}}^{2}}{M_{\psi_{a}}} \right) \right] + (R \to I)\,,
\end{align}
%
where $F(m_{S_{\beta}}^{2}/M_{\psi}^{2}) = m_{S_{\beta}}^{2}\log(m_{S_{\beta}}^{2}/M_{\psi})/(m_{S_{\beta}}^{2}-M_{\psi})$ is the loop function, $M_{\psi_{a}}$ is the fermion mass  and $\chi_{R_{(1,2)}}$ ( $\chi_{I_{(1,2)}}$ ) are the two CP-even (CP-odd) mass eigenstates. To obtain neutrino masses it is necessary that $\mu \neq 0$. In addition, To explain the suppression of the mass matrix, it is usually assumed that the mass of the mediator fermions is very large. Another possibility is small values of $\mu$, this suppress the value of the neutrino masses. The structure of the effective neutrino mass matrix is given by the product $(M_{\nu})_{ij} \propto h_{i a} y_{a j}$, which is similar to the structure of the neutrino mass matrix for the tree-level seesaw mechanism for Dirac neutrinos~\cite{Chulia:2016ngi}. If only one fermion $\psi_R$ is added, we will have two massless neutrinos, which does not agree with the current data obtained from the neutrino experiments~\cite{deSalas:2017kay}. In our case, we will assume the existence of three fermions, generating Dirac scotogenic masses for the two neutrinos ($\nu_{k}$ is massless due to the assignment of charges).

For the Dirac neutrinos the mass matrices are diagonalized by
\begin{align}
(U^{(\nu)}_R)^{\dagger} \mathcal{M}_{\nu} U^{(\nu)}_L = \mathcal{M}_{\nu}^{\text{diag}} = \text{diag}(m_1, m_2, m_3)\,,
\end{align}
where $U^{(\nu)}_R$ and $U^{(\nu)}_L$  are unitary $3 \times 3$ matrices. In the most general Dirac neutrino mass matrices, lepton mixing matrix is
\begin{align}
U_{\text{PMNS}} = (U^{(\ell)}_L)^{\dagger} U^{(\nu)}_L\,.
\end{align}
If we work in the basis where $\ell$ and $\nu_{R}$ are mass eigenstates, the matrices $U_{L}^{(\ell)} = U_{R}^{\nu} = \mathds{1}$. Therefore, we can express the Dirac neutrino mass matrix in the following way
\begin{align}
(\mathcal{M}_{\nu})_{ij} = (U_{\text{PMNS}})_{ij} (\mathcal{M}_{\nu}^{\text{diag}})_{j}\,,
\end{align}
where the matrix $U_{\text{PMNS}}$ is expressed in the standard parameterization as
\begin{align}
U_{\text{PMNS}} = \begin{pmatrix}
    1 & 0		& 0 \\
    0 & c_{23}  & s_{23} \\
    0 & -s_{23} & c_{23}
\end{pmatrix}
\begin{pmatrix}
    c_{13}  &  0 & s_{13}e^{-i\delta} \\
    0 		&  1 & 0 \\
    -s_{13}e^{i\delta} &  0 & c_{13}
\end{pmatrix}
\begin{pmatrix}
    c_{12}  & s_{12} & 0 \\
    -s_{12} & c_{12} & 0 \\
    0		& 0		 & 1
\end{pmatrix}\,,
\end{align}
where $s_{ij} = \sin \theta_{ij}$ and $c_{ij} = \cos \theta_{ij}$ and $\theta_{ij}$ are neutrino mixing angles and $\delta$ is CP-violating phase.

>>>>

On the other hand, we assume that the heavy Majorana fermions are already in the diagonal basis defined as $
\begin{pmatrix}
  \psi_1 &
  \psi_2 &
  \psi_3
\end{pmatrix}^{\operatorname{T}}
$, with masses $M_{\psi_a}$ ($a=1,2,3$).
\section{Neutrinos}
\label{sec:Neutrinos}
%
\begin{figure}
\centering
\includegraphics[scale=0.75]{Neutrino_Loop.pdf}
\caption{One-loop generation of Dirac neutrino mass}
\label{fig:zee}
\end{figure}
%
 The Dirac neutrino mass matrix in this model is generated at one loop-level according to the diagram in  fig.~\ref{fig:zee}. The expression for $\mathcal{M}_{\nu}$ is given by~\cite{Reig:2018mdk}
%
\begin{align}
(\mathcal{M}_{\nu})_{ij} = \frac{\lambda_8 v_S v}{32 \pi^{2}} \sum_{a=1}^{3} \frac{h_{i a} M_{\psi_{a}}y^{\dagger}_{a j}} {m_{\chi_{R_2}}^{2}-m_{\chi_{R_1}}^{2}} \left[ F\left( \frac{m_{\chi_{R_2}}^{2}}{M_{\psi_{a}}} \right) - F\left( \frac{m_{\chi_{R_1}}^{2}}{M_{\psi_{a}}} \right) \right] + (R \to I)\,,
\end{align}
%
%check the following formula:
where $F(x) =x \log x/(x-1)$ is the loop function, $M_{\psi_{a}}$ is
the fermion mass and $\chi_{R_{(1,2)}}$ ( $\chi_{I_{(1,2)}}$ ) are the
two CP-even (CP-odd) mass eigenstates.
To obtain neutrino masses it is necessary that $\mu \neq 0$. In this
way, in addition to the suppression from the seesaw mechanism, we can
have further suppression in the neutrino mass matrix for small values
of $\mu$.
The structure of the effective neutrino mass matrix is given by the
product $(M_{\nu})_{ij} \propto h_{i a} y_{a j}$, which is similar to
the structure of the neutrino mass matrix for the tree-level seesaw
mechanism for Dirac neutrinos~\cite{Chulia:2016ngi}. If only one
fermion $\psi_R$ is added, we will have two massless neutrinos, which
does not agree with the current data obtained from the neutrino
experiments~\cite{deSalas:2017kay}. In our case, we will assume the
existence of three fermions, generating Dirac scotogenic masses for
the two neutrinos ($\nu_{k}$ is massless due to the assignment of
charges).

The mass matrix for Dirac neutrinos is diagonalized by
\begin{align}
(U^{(\nu)}_R)^{\dagger} \mathcal{M}_{\nu} U^{(\nu)}_L = \mathcal{M}_{\nu}^{\text{diag}} = \text{diag}(m_1, m_2, m_3)\,,
\end{align}
where $U^{(\nu)}_R$ and $U^{(\nu)}_L$  are unitary $3 \times 3$ matrices. In the most general Dirac neutrino mass matrices, lepton mixing matrix is
\begin{align}
U_{\text{PMNS}} = (U^{(\ell)}_L)^{\dagger} U^{(\nu)}_L\,.
\end{align}
If we work in the basis where $\ell$ and $\nu_{R}$ are mass eigenstates, the matrices $U_{L}^{(\ell)} = U_{R}^{\nu} = \mathds{1}$. Therefore, we can express the Dirac neutrino mass matrix in the following way
\begin{align}
(\mathcal{M}_{\nu})_{ij} = (U_{\text{PMNS}})_{ij} (\mathcal{M}_{\nu}^{\text{diag}})_{j}\,,
\end{align}
where the matrix $U_{\text{PMNS}}$ is expressed in the standard parameterization as
\begin{align}
U_{\text{PMNS}} = \begin{pmatrix}
    1 & 0		& 0 \\
    0 & c_{23}  & s_{23} \\
    0 & -s_{23} & c_{23}
\end{pmatrix}
\begin{pmatrix}
    c_{13}  &  0 & s_{13}e^{-i\delta} \\
    0 		&  1 & 0 \\
    -s_{13}e^{i\delta} &  0 & c_{13}
\end{pmatrix}
\begin{pmatrix}
    c_{12}  & s_{12} & 0 \\
    -s_{12} & c_{12} & 0 \\
    0		& 0		 & 1
\end{pmatrix}\,,
\end{align}
where $s_{ij} = \sin \theta_{ij}$ and $c_{ij} = \cos \theta_{ij}$ and $\theta_{ij}$ are neutrino mixing angles and $\delta$ is CP-violating phase.
